Baseline centering problem

### 2018-12-19 paper/tangotd.tex

We should find a way to initialize $Z$ so that $Z\approx \Id$ at time
$0$, namely $Z(s,s)=1/\rho(s)$, although starting with $Z(s,s)=1$ should be
quite fine. $Z>0$ (unless we work with $\gamma=1$ and relative stuff
TODO), so the parameterization could reflect that.

@@

>>>>

We should find a way to initialize $Z$ so that $Z\approx \Id$ at time
$0$, namely $Z(s,s)=1/\rho(s)$, although starting with $Z(s,s)=1$ should be
quite fine. (Small initializations of $Z$ are safer.) $Z>0$ (unless we work with $\gamma=1$ and relative stuff
TODO), so the parameterization could reflect that.

@@

Ideally, given the transition $s_3\to s'_3$, I'd like to sample $s_1$ and
$s_2$ proportionally to $Z$ (would cancel the $Z$ factors, and avoid
applying the equation to states that have nothing to do with $s_3$). But
I don't know how to build an efficient sampler from $Z(s_3,\cdot)$.
Something like Metropolis? but this function $Z$ is not constant...
